---
title: "Week 3 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)

cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))

cel <- drop_na(read_csv(url("https://www.dropbox.com/s/4ebgnkdhhxo5rac/cel_volden_wiseman%20_coursera.csv?raw=1")))

```

Following the directions on the Coursera assignment page, you will make four original visualizations. Note that the data for the CCES and CEL data are imported in code in the R Markdown file.

### Put your name here:Chloe Huang

## Exercise 1

Explain what you are visualizing here:
A barplot showing the numbers of correspondents based on their religions. 

Put your figure here:

```{r exercise1,echo=FALSE}
library(ggthemes)

pew_religimp_changed <- recode(cces$pew_religimp,`1`="very Very Important",`2`="Somewhat Important", `3`="Not too Important", `4`="Not at all Important")

cces <- add_column(cces,pew_religimp_changed)

cces %>% ggplot(aes(x=pew_religimp_changed,fill=pew_religimp_changed))+
  geom_bar(position="dodge")+
  labs(x="Religion",y="Count")+
   guides(fill=FALSE)+
  scale_fill_wsj() + theme_wsj() +
  annotate("text",x=4,y=320,label="Most Voted",color="Black")
  

```

## Exercise 2

Explain what you are visualizing here:Congress members Roe Roberts and Pepper, Claude are the two congressmen who have been brought in bills quite a lot. This chart would like to compare the all bills them brought in congress.

Put your figure here:

```{r exercise2,echo=FALSE}

cel_changed_male<-filter(cel, female==0)
cel_changed_male<-cel_changed_male%>%arrange(desc(cel_changed_male$all_bills))

cel_compare<-filter(cel, thomas_name %in% c("Roe, Robert", "Pepper, Claude"))
ggplot(cel_compare,(aes(x=congress,y=all_bills,color=thomas_name)))+geom_line()+facet_wrap(~thomas_name)+theme(legend.position="none")

```

## Exercise 3

Explain what you are visualizing here:This Chart Compare the  professional specialty of legislature against the number of bills passed in the 115th congress.

Put your figure here:

```{r exercise3,echo=FALSE}
library(ggrepel)
library(RColorBrewer)


cel$female_change <- recode(cel$female,`1`="Female",`0`="Male")

cel %>% filter(congress==115) %>% 
  ggplot(aes(x=state_leg_prof,y=all_pass, color=female_change))+
  geom_point()+
  geom_text_repel(data=filter(cel,congress==115 & all_pass>10),mapping=aes(x=state_leg_prof,y=all_pass,label=thomas_name))+scale_color_brewer(name="Gender",palette="Dark2")+ labs(x="Professional",y="Bills Passed")




```

## Exercise 4

Explain what you are visualizing here:

Put your figure here:Compare difference between female and male in terms of family incomes. 

```{r exercise4,echo=FALSE}

cces$gender_changed <- recode(cces$gender,`1`="Male",`2`="Female")
ggplot(cces,aes(x=faminc_new,fill=gender_changed,color=gender_changed))+
  geom_histogram( position="identity",alpha=0.5)+theme(legend.title = element_blank(),legend.position="top")+  labs(x="Income Level",y="Number of Family")

```
