---
title: "Week 2 Peer Review"
output: html_document
---

```{r setup, include=FALSE}

######DO NOT MODIFY. This will load required packages and data.

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
cces <- drop_na(read_csv(url("https://www.dropbox.com/s/ahmt12y39unicd2/cces_sample_coursera.csv?raw=1")))
```

Your objective is to replicate these figures, created using the Cooperative Congressional Election Study data. These figures are similar to those we completed in the lecture videos.

### Put your name here:Chloe Huang



## Exercise 1

Hints:

* For the x-axis, use the variable "ideo5".

* Make sure you recode the data for the "ideo5" variable to generate the correct names for the x-axis. You will want to consult the codebook.

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Use guides() to drop the legend.

* Make sure the axis labels and figure title are correct.


```{r exercise1,echo=FALSE}
ideo5_changed <- recode(cces$ideo5,`1`="very liberal",`2`="liberal", `3`="moderate", `4`="conservative", `5`="very conservative")

cces <- add_column(cces,ideo5_changed)

cces %>% ggplot(aes(x=ideo5_changed,fill=ideo5_changed))+
  geom_bar()+
  labs(x="Ideology",y="Count")+
   guides(fill=FALSE)

```

## Exercise 2

Hints:

* For the x-axis, use the variable "pew_religimp".

* Make sure you recode the data for the "pew_religimp" variable to generate the correct labels for the x-axis. You will want to consult the codebook.

* Rename the column for Ideology to make sure the first letter is upper-case (to make the legend appear correctly).

* Use the fill aesthetic to have R fill in the bars. You do not need to set the colors manually.

* Make sure the axis labels and figure title are correct.

```{r exercise2,echo=FALSE}
pew_religimp_changed <- recode(cces$pew_religimp,`1`="Very Important",`2`="Somewaht Important", `3`="Not Too Important", `4`="Not At All Important")

cces <- add_column(cces,pew_religimp_changed)

cces %>% ggplot(aes(x=pew_religimp_changed,fill=ideo5_changed))+
  geom_bar()+
  labs(x="Important of Religion",y="Count")
```

## Exercise 3

Instructions:

* For this visualization, you are creating your own data for practice.

* Create a tibble/data frame with three columns: Semester, Student, and Grade.

* There should be six semesters and three students (Amanda, Betty, and Carol)

* Create grades for the students using the runif() command, with values between 80 and 100. Hint: you'll need 18 grades total.

The figure should look approximately like this (your vaules will be slightly different):


```{r exercise3,echo=FALSE}
Student<-c("Amanda","Betty", "Carol")
Semester<-c(1:6)
School <- expand.grid(stu=Student, sem=Semester)
grade<- runif(18, 80,100)
School$Grade<-grade


ggplot(School,(aes(x=sem,y=Grade,color=stu)))+geom_line()+  facet_wrap(~stu)+theme(legend.position="none")


```
